---
title: "Suits Viewership Analysis"
author: "Yücel Tan Ebiri"
format: html
execute:
  echo: false
  warning: false
  message: false
---

# Introduction

*Suits* is an American legal drama television series that premiered in 2011.

The show follows talented lawyer Harvey Specter and Mike Ross, a brilliant college dropout with exceptional memory skills.

# Data

```{r}
library(ggplot2)

season <- c(1,2,3,4,5,6,7,8,9)
viewers <- c(4.6,4.2,3.7,3.5,3.0,2.5,2.0,1.5,1.0)

tv_data <- data.frame(season, viewers)
tv_data$change <- c(NA, diff(tv_data$viewers))
```

# Summary Statistics

```{r}
summary(tv_data$viewers)
```

```{r}
ggplot(tv_data, aes(x = season, y = viewers)) +
  geom_line() +
  geom_point(size = 3) +
  labs(
    title = "Suits Viewership by Season",
    x = "Season",
    y = "Average Viewers (millions)"
  ) +
  theme_minimal()
```

```{r}
ggplot(tv_data[-1, ], aes(x = season, y = change)) +
  geom_col() +
  labs(
    title = "Season-to-Season Change in Viewership",
    x = "Season",
    y = "Change in Viewers"
  ) +
  theme_minimal()
```

# Interpretation

The audience for *Suits* gradually decreased over time.

The show had its highest average audience in Season 1 with around 4.6 million viewers and its lowest audience in Season 9 with around 1 million viewers.

The biggest drop happened after Season 7.
